Scalar Feedback based Joint Time-Frequency Precoder Interpolation for MIMO-OFDM Systems

### 2020-04-26 paper/main.tex
adding changes

\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.5\baselineskip}
\def\imwidth{0.625}
%package list
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

@@

\vspace{-0.5\baselineskip}
\subsection{Differential quantization and channel tracking}
\label{quantiz}
For channels that vary slowly with time, adaptive differential
quantization is an effective method for tracking parameters over time
using very few bits (often just one bit per parameter). For example,
while tracking a slowly varying discrete random process $x_n$ at time
$n$, the one bit can be used to determine the direction in which to
move in order to track the parameter. This can be denoted by
$\beta_{n} = \mbox{sign}(x_{n} - \hat{x}_{n-1})$, where $x_n$ is the
unquantized (accurate) value and $\hat{x}_{n-1}$ is the quantized
value. Further, the step size for the move can be adapted based on the
speed of channel variation as well the accuracy needed. If $\Delta_n$
is the step size, we define our adaptive quantizer as
\begin{equation}
\hat{x}_{n} = \hat{x}_{n-1} + \beta_{n}\Delta_{n} \mbox{ where }
\label{delta_eqn}
\Delta_{n} = \begin{cases}
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}\\
    \Delta_{n-1}/M , & \text{if $\beta_{n} \neq \beta_{n-1}$}.
  \end{cases}
\end{equation}
where $M$ is the scaling factor used during the positive and negative
moves. We initialize $\Delta_1$ as $\Delta_1 = |x_{2}-\hat{x}_1|$. This is performed separately for each of the quantized
parameters.

@@

\vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. To construct precoders for the rest of the subcarriers, we will use
precoder parameters from both the ``past'' and ``future'' time
instances to do the interpolation (using backtracking to ensure
causality). When using future time instances, the implication is that the precoder
estimation is improved at a later time instant i.e. after receiving
the feedback of the next set of subcarriers. Note that the precoder
used for transmission is causally obtained, while the ``future''
correction of past precoders merely improves the interpolation
accuracy. In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated
using the neighbouring subcarriers using bilinear interpolation
(equivalent to linear interpolation in two dimensions). These
interpolated values are then used to reconstruct the precoding
matrices all together by applying the reverse transformation of
breaking the precoder into independent parameters as given in
Equation~\ref{eq:decompose}. Thus, the approach here is able to
exploit the time and frequency correlation jointly to enhance
performance.

@@

% Using the idea of joint interpolation given in the other paper.
\vspace{-1\baselineskip}
\section{Conclusion}
\label{section4}
We have presented a predictive quantization based precoder
reconstruction for MIMO-OFDM systems that employs scalar quantization
based feedback of precoder parameters. Quantizing and adapting the
Givens rotation and Householder transformation parameters of precoders
minimizes receiver feedback to the transmitter while permitting
effective precoder adaptation. Exploiting temporal and frequency
correlations jointly enhances performance significantly. Simulations
reveal that the proposed approach converges faster and has smaller
errors when compared to manifold based approaches. Our feedback
approach, with simple 2D-interpolation over the scalar parameters,
tracks precoders effectively. Future work would involve tuning the
adaptation rates of scalar parameters and further reduction of
redundancies to improve quantization.

\vspace{-10pt}
% \section{Acknowledgment}

>>>>

\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.5\baselineskip}
\def\imwidth{0.7}
%package list
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

@@

% \vspace{-0.5\baselineskip}
\subsection{Differential quantization and channel tracking}
\label{quantiz}
For channels that vary slowly with time, adaptive differential
quantization is an effective method for tracking parameters over time
using very few bits (often just one bit per parameter). For example,
while tracking a slowly varying discrete random process $x_n$ at time
$n$, the one bit can be used to determine the direction in which to
move in order to track the parameter. This can be denoted by
$\beta_{n} = \mbox{sign}(x_{n} - \hat{x}_{n-1})$, where $x_n$ is the
unquantized (accurate) value and $\hat{x}_{n-1}$ is the quantized
value. Further, the step size for the move can be adapted based on the
speed of channel variation as well the accuracy needed. If $\Delta_n$
is the step size, we define our adaptive quantizer as
\begin{equation}
\hat{x}_{n} = \hat{x}_{n-1} + \beta_{n}\Delta_{n} \mbox{ where }
\label{delta_eqn}
\Delta_{n} = \begin{cases}
    M \Delta_{n-1}, & \text{if $\beta_{n} = \beta_{n-1}$}\\
    \Delta_{n-1}/M , & \text{if $\beta_{n} \neq \beta_{n-1}$}.
  \end{cases}
\end{equation}
where $M$ is the scaling factor used during the positive and negative
moves. We initialize $\Delta_1$ as $\Delta_1 = |x_{2}-\hat{x}_1|$. This is performed separately for each of the quantized
parameters.

@@

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy. 
In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated
using the neighbouring subcarriers using bilinear interpolation
(equivalent to linear interpolation in two dimensions). These
interpolated values are then used to reconstruct the precoding
matrices all together by applying the reverse transformation of
breaking the precoder into independent parameters as given in
Equation~\ref{eq:decompose}. Inorder to improve the precoder estimates 
and interpolation accuracy we walkback to improve the past estimates by interpolating
upon the current estimates. Thus, the approach here is able to exploit the time and frequency correlation jointly to enhance performance.
% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%

@@

% Using the idea of joint interpolation given in the other paper.
% \vspace{-1\baselineskip}
\section{Conclusion}
\label{section4}
We have presented a predictive quantization based precoder
reconstruction for MIMO-OFDM systems that employs scalar quantization
based feedback of precoder parameters. Quantizing and adapting the
Givens rotation and Householder transformation parameters of precoders
minimizes receiver feedback to the transmitter while permitting
effective precoder adaptation. Exploiting temporal and frequency
correlations jointly enhances performance significantly. Simulations
reveal that the proposed approach converges faster and has smaller
errors when compared to manifold based approaches. Our feedback
approach, with simple 2D-interpolation over the scalar parameters,
tracks precoders effectively. Future work would involve tuning the
adaptation rates of scalar parameters and further reduction of
redundancies to improve quantization.

% \vspace{-10pt}
% \section{Acknowledgment}
